Summer 2024 Report

### 2025-01-22 Relations/Report.tex

\begin{table}[h!]
  \centering
  \caption{Local implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, WR  & CR, SR  &   &   &   \\
  \hline
  \textbf{RP} & CR, WR  & CR, SR  &   &   &   \\
  \hline
  \textbf{NP} & NP, WR  & CR, WN  &   &   &   \\
  \hline
  \textbf{UN} & UN, WR  & UN, WN  &   &   &   \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Local implications - Counterexamples}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, CE-6  & WIP , CE-9  &   &   \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, CE-6  & WIP , CE-9 &   &   \\
  \hline
  \textbf{NP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 &   &   \\
  \hline
  \textbf{UN} & CE-3, CE-9  & CE-3, CE-6  & CE-3, CE-9  &   &   \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table} 
\sacomment{We can potentially merge the two tables. Is it the case that we never move one step up the hierarchy? Is it always a case that if we move one step we move up all the steps, if that is the case then we just need to either express the relevant counterexample, or express the property attained.}

>>>>

\begin{table}[h!]
  \centering
  \caption{Local implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, WR  & CR, SR  & CR?, SR  &   &   \\
  \hline
  \textbf{RP} & CR, WR  & CR, SR  & CR?, SR &   &   \\
  \hline
  \textbf{NP} & NP, WR  & CR, WN  & NP, SR  &   &   \\
  \hline
  \textbf{UN} & UN, WR  & UN, WN  & UN, SR  & UN, WN$\land$SR  &   \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Local implications - Counterexamples}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, CE-6  & WIP , CE-9  &   &   \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, CE-6  & WIP , CE-9 &   &   \\
  \hline
  \textbf{NP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 &   &   \\
  \hline
  \textbf{UN} & CE-3, CE-9  & CE-3, CE-6  & CE-3, CE-9  & CE-3, CE-3  &   \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table} 
\sacomment{We can potentially merge the two tables. Is it the case that we never move one step up the hierarchy? Is it always a case that if we move one step we move up all the steps, if that is the case then we just need to either express the relevant counterexample, or express the property attained.}
